### 2020-09-16 priority-gv.tex
Renamed SC rules, added PCP-SC.
Added reduction for PCP.
Minor changes.

\subsubsection{Structural congruence}
\[
\begin{array}{llcl}
  \LabTirName{E-LnkComm}  & \tm{\plug{\conf{F}}{\link\;{\pair{x}{y}}}}
                          & \equiv & \tm{\plug{\conf{F}}{\link\;{\pair{y}{x}}}}
  \\
  \LabTirName{E-ResComm}  & \tm{\res{x}{y}{\res{z}{w}{\conf{C}}}}
                          & \equiv & \tm{\res{z}{w}{\res{x}{y}{\conf{C}}}}
  \\
  \LabTirName{E-ParAssoc} & \tm{\ppar{\conf{C}}{(\ppar{\conf{D}}{\conf{E}})}}
                          & \equiv & \tm{\ppar{(\ppar{\conf{C}}{\conf{D}})}{\conf{E}}}
  \\
  \LabTirName{E-ParComm}  & \tm{\ppar{\conf{C}}{\conf{D}}}
                          & \equiv & \tm{\ppar{\conf{D}}{\conf{C}}}
  \\
  \LabTirName{E-Garbage}  & \tm{\ppar{\conf{C}}{\child{\unit}}}
                          & \equiv & \tm{\conf{C}}
  \\
  \LabTirName{E-ScopeExt} & \tm{\res{x}{y}{(\ppar{\conf{C}}{\conf{D}}})}
                          & \equiv & \tm{\ppar{\conf{C}}{\res{x}{y}{\conf{D}}}},
                                     \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{\conf{C}})}
\end{array}
\]

\subsubsection{Configuration reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-New}   & \tm{\plug{\conf{F}}{\new\;\unit}}
                         & \cred & \tm{\res{x}{y}{\plug{\conf{F}}{\pair{x}{y}}}}
    \\
    \LabTirName{E-Spawn} & \tm{\plug{\conf{F}}{\spawn\;V}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\child{(V\;\unit)}}}
    \\
    \LabTirName{E-Send}  & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\send\;{\pair{V}{x}}}}
                           {\plug{\conf{F'}}{\recv\;{y}}})}}
                         & \cred & \tm{\res{x}{y}{(\ppar
                                   {\plug{\conf{F}}{x}}
                                   {\plug{\conf{F'}}{\pair{V}{y}}})}}
    \\
    \LabTirName{E-Close} & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\wait\;{x}}}
                           {\plug{\conf{F'}}{\close\;{y}}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\plug{\conf{F'}}{\unit}}}
  \end{array}
  \\
  \inferrule*[lab=E-LiftC]{
    \tm{\conf{C}}\cred\tm{\conf{C'}}
  }{\tm{\plug{\conf{G}}{\conf{C}}}\cred\tm{\plug{\conf{G}}{\conf{C'}}}}

@@

  \inferrule*[lab=E-LiftE]{
    \tm{\conf{C}}\equiv\tm{\conf{C'}}
    \\
    \tm{\conf{C'}}\cred\tm{\conf{D'}}
    \\
    \tm{\conf{D'}}\equiv\tm{\conf{D}}
  }{\tm{\conf{C}}\cred\tm{\conf{D}}}
\end{mathpar}

@@

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    $\tm{M}$ is a value;
  \item[Step]
    There exists some $\tm{N}$ such that $\tm{M}\tred\tm{N}$; or
  \item[Blocked] \label{lem:pgv-progress-terms:blocked}
    There exists some $\tm{E}$ and $\tm{R}$ such that $\tm{M}=\tm{\plug{E}{R}}$.
  \end{description}
\end{restatablelemma}
\begin{proof}
  \todo{Write proof.}
\end{proof}

\begin{restatabletheorem}{thmpgvopenprogressconfs}[Open Progress, $\cred$]
  \label{thm:pgv-open-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\main\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \item[Blocked]
    There exist $\tm{x_i}$ and $\tm{y_i}$ for $0\leq{i}\leq{n}$, and $\tm{\phi_j}$ and $\tm{R_j}$ for $0\leq{j}\leq{m}$, such that $\tm{\conf{C}}=\tm{\res{x_1y_1\dots x_ny_n}{}{(\phi_1R_1 \parallel\dots\parallel \phi_mR_m)}}$ and for each $\tm{R_j}$ there exists some $\tm{a_j}\in\fn(\ty{\Gamma})$ such that $\blocked(\tm{a_j},\tm{R_j})$.
  \end{description}
\end{restatabletheorem}
\begin{proof}
  \todo{Write proof.}
\end{proof}

>>>>

\subsubsection{Structural congruence}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{SC-LinkSwap}   & \tm{\plug{\conf{F}}{\link\;{\pair{x}{y}}}}
                               & \equiv & \tm{\plug{\conf{F}}{\link\;{\pair{y}{x}}}}
    \\
    \LabTirName{SC-ResSwap}    & \tm{\res{x}{y}{\conf{C}}}
                               & \equiv & \tm{\res{y}{x}{\conf{C}}}
    \\
    \LabTirName{SC-ResComm}    & \tm{\res{x}{y}{\res{z}{w}{\conf{C}}}}
                               & \equiv & \tm{\res{z}{w}{\res{x}{y}{\conf{C}}}}
    \\
    \LabTirName{SC-ResExt}     & \tm{\res{x}{y}{(\ppar{\conf{C}}{\conf{D}}})}
                               & \equiv & \tm{\ppar{\conf{C}}{\res{x}{y}{\conf{D}}}},
                                          \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{\conf{C}})}
    \\
    \LabTirName{SC-ParNil}     & \tm{\ppar{\conf{C}}{\child{\unit}}}
                               & \equiv & \tm{\conf{C}}
    \\
    \LabTirName{SC-ParComm}    & \tm{\ppar{\conf{C}}{\conf{D}}}
                               & \equiv & \tm{\ppar{\conf{D}}{\conf{C}}}
    \\
    \LabTirName{SC-ParAssoc}   & \tm{\ppar{\conf{C}}{(\ppar{\conf{D}}{\conf{E}})}}
                               & \equiv & \tm{\ppar{(\ppar{\conf{C}}{\conf{D}})}{\conf{E}}}
  \end{array}
\end{mathpar}

\subsubsection{Configuration reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-New}   & \tm{\plug{\conf{F}}{\new\;\unit}}
                         & \cred & \tm{\res{x}{y}{(\plug{\conf{F}}{\pair{x}{y}})}}
    \\
    \LabTirName{E-Spawn} & \tm{\plug{\conf{F}}{\spawn\;V}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\child\;V\;\unit}}
    \\
    \LabTirName{E-Send}  & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\send\;{\pair{V}{x}}}}
                           {\plug{\conf{F'}}{\recv\;{y}}})}}
                         & \cred & \tm{\res{x}{y}{(\ppar
                                   {\plug{\conf{F}}{x}}
                                   {\plug{\conf{F'}}{\pair{V}{y}}})}}
    \\
    \LabTirName{E-Close} & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\wait\;{x}}}
                           {\plug{\conf{F'}}{\close\;{y}}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\plug{\conf{F'}}{\unit}}}
  \end{array}
  \\
  \inferrule*[lab=E-LiftC]{
    \tm{\conf{C}}\cred\tm{\conf{C'}}
  }{\tm{\plug{\conf{G}}{\conf{C}}}\cred\tm{\plug{\conf{G}}{\conf{C'}}}}

@@

  \inferrule*[lab=E-LiftSC]{
    \tm{\conf{C}}\equiv\tm{\conf{C'}}
    \\
    \tm{\conf{C'}}\cred\tm{\conf{D'}}
    \\
    \tm{\conf{D'}}\equiv\tm{\conf{D}}
  }{\tm{\conf{C}}\cred\tm{\conf{D}}}
\end{mathpar}

@@

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    $\tm{M}$ is a value;
  \item[Step]
    There exists some $\tm{N}$ such that $\tm{M}\tred\tm{N}$; or
  \item[Blocked]
    There exists some $\tm{E}$ and $\tm{R}$ such that $\tm{M}=\tm{\plug{E}{R}}$.
  \end{description}
\end{restatablelemma}
\begin{proof}
  \todo{Write proof.}
\end{proof}

\begin{restatabletheorem}{thmpgvopenprogressconfs}[Open Progress, $\cred$]
  \label{thm:pgv-open-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \item[Blocked]
    There exist $\tm{x_i}$ and $\tm{y_i}$ for $0\leq{i}\leq{n}$, and $\tm{\phi_j}$ and $\tm{R_j}$ for $0\leq{j}\leq{m}$, such that $\tm{\conf{C}}=\tm{\res{x_1y_1\dots x_ny_n}{}{(\phi_1R_1 \parallel\dots\parallel \phi_mR_m)}}$ and for each $\tm{R_j}$ there exists some $\tm{a_j}\in\fn(\ty{\Gamma})$ such that $\blocked(\tm{a_j},\tm{R_j})$.
  \end{description}
\end{restatabletheorem}
\begin{proof}
  \todo{Write proof.}
\end{proof}
